Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-14 cvpr2018.tex

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions. We propose an effective end-to-end single-stream network that can generate photographic high-resolution images. Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g. a ${11.86}$ Inception score on COCO). 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a translation from a semantic text embedding space to a complex RGB image space. This task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts in descriptions but also fine-grained descriptive details in image pixels. 
However, insufficient methods are developed to successfully address this task due to its particular challenges.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, StackGAN  \cite{han2017stackgan} is a successful method that stacks another low-to-high resolution GAN to generate high-quality $256^2$ images, with two training stages. Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images but treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training $128^2$ image conditioned on a targeting description. But its high-resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in a fully end-to-end manner is still an open and attractive question.

%We outline several empirical reasons for the challenges of 
Text-to-image synthesis using GANs has two main difficulties. The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
To guarantee the image diversity and semantic consistency,
we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.
This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
%% It is a regularization to limit the discriminators to use unexpected information to make decision.

@@

Deep generative models attract wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise. The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution. $G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.

@@

For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $ \mathcal{Y}$ contains a set of training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
%%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to images and preserve these image structures. Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully enjoy top-down knowledge from discriminators for higher resolutions. We can observe consistent image structures and styles in both low and high resolutions.
We think such consistency is able to reduce the model instability.
As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
%% %We present the following multi-purpose adversarial loss to support more effective generator training.

@@

To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.

The pair loss is designed to guarantee the global semantic consistency. However, there is no explicit loss that forces the discriminator to differentiate pure real images from fake images. As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
%However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
%Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging. 
%Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain unexpected image features and lead to artifacts.

@@

\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following loss\footnote{The objective of the generator is omitted as it can be easily inferred.}:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{L}(& \mathcal{G}, \mathcal{D})  = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
\end{split}
\end{equation}
where $L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =x^2$. For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}). $R=1$ refers to the (largest local) global range. For the matching-aware pair loss, 
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

@@

3) Visual-semantic similarity. The aforementioned metrics are widely used for general GANs. The problem of them is that they can not measure the alignment between the generated images and conditioned text. We introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}. Denote $\bm{v}$ as the image feature vector extracted by a Inception CNN.
We define a scoring function $C(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
Then, we learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
\begin{equation}\vspace{-.2cm}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta- C(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{v}} }~\max( 0,  \delta- C(f_t(\bm{t}), f_v( \bm{v}_{\overline{v}} )))
\end{split}
\vspace{-.2cm}
\end{equation}
where $\delta$ is the margin, which is set as 0.2. $\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{v}}, \bm{t} \}$ denote mismatched image-text pairs. In the testing stage, given an text embedding $\bm{t}$, and the generated image encoded by the Inception-CNN $\bm v$, the VS score is calculated as $C(\bm v, \bm{t})$. Higher score indicates better semantic consistency, i.e. stronger alignment between generated images and conditioned text.

@@

\begin{table}[t] % retrieval
	\small
	\begin{center}
		\begin{tabularx}{.475\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
			&	 CUB		&	Oxford-102  & COCO		     \\ \hline
			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  -		\\ 
			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
		\end{tabularx} 
	\end{center}
	\vspace{-.4cm}
	\caption{The VS similarity evaluation on the three datasets. The higher score represents higher semantic consistency between the generated images and the text information. The groundtruth score is shown in the first row.} \label{table:vss} \vspace{-.3cm}
\end{table}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioning on semantic image descriptions. We propose an effective end-to-end single-stream network that can generate photographic high-resolution images. \textcolor{red}{Our method leverages deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games} inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to improve the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, thus alleviates the needs of human evaluation. 
With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics (e.g. a ${11.86}$ Inception score on COCO). 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from one semantic text embedding space to one complex RGB image space. This task requires the generated images to be not only realistic but also \textit{semantically consistent}.
%i.e., the generated images not only preserve object sketch, color information in descriptions but also fine-grained descriptive details in image pixels. 
However, this problem still remains unsolved due to its particular challenges. 
%insufficient methods are developed to successfully address this task due to its particular challenges.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scale up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy, which stacks another low-to-high resolution GAN to generate high-resolution $256^2$ images. Later on, \cite{dong2017semantic} proposes to bypass the difficult of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}. It works by re-rendering an arbitrary-style $128^2$ training  image conditioned on a targeting description. However, its high-resolution synthesis capability remains unclear.

At present,\textcolor{red}{adversarial training of a generative model mapping a low-dimensional semantic space to  high-resolution and diverse images space in a fully end-to-end manner is still an open question. }

%We outline several empirical reasons for the challenges of 
Text-to-image synthesis using GANs has two main difficulties. \textcolor{red}{The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}.} %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla GAN, without requiring any multiple internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a novel convolutional neural network (CNN) framework for the generator to \textcolor{red}{cooperate with} our nested discriminators more effectively.
To guarantee the image diversity and semantic consistency,
we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain \textcolor{red}{receptive field. This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty.}%focal ranges

%To alleviate the need for manual human evaluation about the matching between generated images and text description, we propose to learn a visual-semantic embedding model, thus providing a measure for quantitative evaluation of the image sentence consistency.
%% It is a regularization to limit the discriminators to use unexpected information to make decision.

\textcolor{red}{To summarize, our contributions are:}

@@

Deep generative models have attracted wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate fake images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise. The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution. $G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$.

@@

For each side output $X_i$, we propose to apply a distinct discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  %\text{where} \;\;	 \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $\mathcal{D}  =  \{D_1, ..., D_s\} $, and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), where each focus on learning diverse discriminative features in different contextual scales.
%%Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to images and preserve these image structures. Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully enjoy top-down knowledge from discriminators for higher resolutions. We can observe consistent image structures and styles in both low and high resolutions.
We think such consistency is able to reduce the model instability.
As an evidence, we can obtain significantly more consistent results exhibited in both low- and high-resolution outputs compared with StackGAN (see experiments). 
%% %We present the following multi-purpose adversarial loss to support more effective generator training.

@@

To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatched text and fake image with conditioned text.

The pair loss is designed to guarantee the global semantic consistency. However, there is no explicit loss that forces the discriminator to differentiate pure real images from fake images. Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging.  Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.
%As the image resolution goes higher, discriminators might loss focus for local fine-grained image details.
%However, this loss has two major weaknesses. First, there is no explicit loss that force the discriminator to differentiate real images from fake images. 
%Combining both tasks (generating realistic images and matching image with text) into one output further complicates the learning tasks, which is already challenging. 
%Second, as the image resolution goes higher, it might be challenging for a global pair-loss discriminator to capture local fine-grained details.  
In addition, as pointed in \cite{shrivastava2016learning}, a single global discriminator may over-emphasize certain unexpected image features and lead to artifacts.

@@

\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following loss\footnote{The objective of the generator is omitted as it can be easily inferred.}:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{L}(& \mathcal{G}, \mathcal{D})  = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
\end{split}
\end{equation}
where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}). $R=1$ refers to the (largest local) global range. For the matching-aware pair loss, 
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

@@

3) \textbf{Visual-semantic similarity.} The aforementioned metrics are widely used for general GANs. The problem of them is that they can not measure the alignment between the generated images and conditioned text. We introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}. Denote $\bm{v}$ as the image feature vector extracted by a pre-trained Inception model $f_{cnn}$\cite{inception}.
We define a scoring function $c(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
Then, we learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into a common space in $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
%\mathcal{L}_{vs} &=
\begin{equation}\vspace{-.2cm}
\begin{split}
 & \sum_{ \bm{v} }\sum_{ \bm{t}_{\overline{v}} }~\max( 0, \delta  - c(f_v(\bm{v}), f_t( \bm{t}_{{v}}) )+ c(f_v(\bm{v}), f_t( \bm{t}_{\overline{v}}) )     ) \\
 & + \sum_{ \bm{t} }\sum_{ \bm{v}_{\overline{t}} }~\max( 0,  \delta  - c(f_t(\bm{t}), f_v( \bm{v}_{{v}} )) +  c(f_t(\bm{t}), f_v( \bm{v}_{\overline{t}} ))  )
\end{split}
\vspace{-.2cm}
\end{equation}
where $\delta$ is the margin, which is set as 0.2. $\{\bm{v}, \bm{t}\}$ is a ground truth image text pair, and $\{\bm v, \bm t_{\overline{v}} \}$ and $\{ \bm v_{\overline{t}}, \bm{t} \}$ denote mismatched image-text pairs. In the testing stage, given an text embedding $\bm{t}$, and the generated image $\bm{x}$, the VS score is calculated as $c(f_{cnn}(\bm{x}), \bm{t})$. Higher score indicates better semantic consistency, i.e. stronger alignment between generated images and conditioned text.

@@

\begin{table}[t] % retrieval
	\small
	\begin{center}
		\begin{tabularx}{.475\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
			&	 CUB		&	Oxford-102  & COCO		     \\ \hline
			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\ 
			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.199{\pm}.183}$  \\ \hline
		\end{tabularx} 
	\end{center}
	\vspace{-.4cm}
	\caption{The VS similarity evaluation on the three datasets. The higher score represents higher semantic consistency between the generated images and the text information. The groundtruth score is shown in the first row.} \label{table:vss} \vspace{-.3cm}
\end{table}

### 2017-11-14 supp.tex

%%%%%%%%% BODY TEXT
\begin{appendices}
%\renewcommand{\thechapter}{A\arabic{chapter}}
\section{Results on the CUB bird dataset}

@@

%{\small
%	\bibliographystyle{ieee}
%	\bibliography{egbib}
%}

>>>>

%%%%%%%%% BODY TEXT
\begin{appendices}

\section{Training Details}
%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
The Adam optimizer is used for all experiments.  The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (50 for COCO). The CUB and Oxford-102 datasets are trained for 500 epochs in total (200 epochs for COCO).
For the local image loss, we set $R=1$ and for $64^2$ and $128^2$ side outputs and $R=5$ for $256^2$ and $512^2$ outputs.

All intermediate conv layers except from the specified ones for both generators and discriminators use $3{\times}3$ kernels (with reflection padding).
We also experimented other normalization (i.e. instance normalization \cite{ulyanov2016instance} and layer normalization \cite{ba2016layer}) used by recent advances \cite{zhu2017unpaired,chen2017photographic}. Both are not satisfactory.

We use 1-repeat residual block for the generator till $256^2$ resolution. The input of the generator is a $1024{\times}4{\times}4$ tensor. As the feature map size increases, the number of feature maps is downsampled by $2$ at $8, 32, 128, 256$ sizes in generator. 
To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory. We use $3$-repeat res-block followed by the stretching and linear compression layer. 
Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.

%\renewcommand{\thechapter}{A\arabic{chapter}}
\section{Results on the CUB bird dataset}

@@

{\small
	\bibliographystyle{ieee}
	\bibliography{reference_zizhao,egbib}
}
